Adaptive Scheduling of Scientific Workflows

### 2024-04-15 main.tex
further corrected and improved the description of the implementation

In this case ($Res <0$), we  try evicting
some data from memory so that we have enough memory to execute task~$v$. 
We need to evict at least $Res$ data.
For now, we propose a greedy approach, evicting the smallest files of $\PD_j$ until $Res$ data has been evicted,
in order to avoid costly communications. 
\AB{FYI We initially discussed  evicting the largest files, but this leads to 
large communications and does not seem efficient after all... Maybe we can think of another 
approach that would take into account both data size and bottom level...}
While tentatively evicting files, we remove them from the list of pending memories and move them into a list
    of memories pending in the communication buffer.
We keep track of the available buffer size, too.

@@

\smallskip
\noindent{\bf Step 3.} We tentatively assign task~$v$ on $p_j$. Its starting time $st_v$
is dictated by the maximum between $rt_j$, and all communications that
must be orchestrated from predecessor tasks $u\notin T(p_j)$. Its
finish time on $p_j$ is then 
$FT(v,p_j) = st_v + \frac{w_v}{s_j}$.
    \skug {TODO PUT THE FORMULA HERE}

@@

    \textbullet For every predecessor of~$v$ that has been assigned to another processor, we

@@

    \textbullet
We adjust ready times on communication buffers $rt_{j, j'}$ for every predecessor processor $u$ of $v$: we increase them by the
    communication time $c(v, u) / \beta$.

>>>>

In this case ($Res <0$), we  try evicting
some data from memory so that we have enough memory to execute task~$v$. 
We need to evict at least $Res$ data.
For now, we propose a greedy approach, evicting the smallest files of $\PD_j$ until $Res$ data has been evicted,
in order to avoid costly communications. 
\AB{FYI We initially discussed  evicting the largest files, but this leads to 
large communications and does not seem efficient after all... Maybe we can think of another 
approach that would take into account both data size and bottom level...}
While tentatively evicting files, we remove them from the list of pending memories and move them into a list
    of memories pending in the communication buffer.
We keep track of the available buffer size, too - each time a file gets moved into the pending in buffer, the available buffer size is reduced by its weight.

@@

\smallskip
\noindent{\bf Step 3.} We tentatively assign task~$v$ on $p_j$.
    Its starting time $st_v$
is dictated by the maximum between $rt_j$, and all communications that
must be orchestrated from predecessor tasks $u\notin T(p_j)$.
    The starting time is then
    \[ST(v, p_j) = \max{ \{rt_j, \max_{ u \in \Pi(v)}\{ FT(u)+ c_{u,v} / \beta , rt_{proc(u), p_j} + c_{u,v} / \beta  \} \} } \]
    Its finish time on $p_j$ is then
$FT(v,p_j) = st_v + \frac{w_v}{s_j}$.

@@

    \textbullet For every predecessor of~$v$ that has been assigned to another processor, we adjust ready times on
    communication buffers $rt_{j', j}$ for every predecessor $u$'s processor $j'$: we increase them by the
    communication time $c( u,v) / \beta$.

@@
